### 2019-02-08 2-Chapters/1-Chapter/chapter1.tex
Version 0.1

@@

@@

>>>>

\subsection{Spectrum scarcity}

\subsection{Low-consumption IoT devices for the future}

@@

\subsection{Online/sequential machine learning to automatically improve wireless communications on the run}

\subsection{Example: Opportunistic Spectrum Access (OSA) in licensed bands}

\subsection{Example: decentralized learning in unlicensed bands with selfish or orthogonalization-based MAB algorithms}

@@

- Literature review of stochastic bandit algorithms (here)

- Aggregation of algorithms for online algorithm selection, state-of-the-art empirical performance with \textbf{Aggregator} (WCNC 2018)

- The most complete open-source simulation library for MAB problems, SMPyBandits (JMLR MLOSS and GitHub)

- Different models for MAB learning for IoT networks (CROWNCOM 2017, ICT demo 2018, WCNC 2019 and MOTIoN 2019)

- A refined analysis and a new impulse on multi-player bandits (ALT 2018, and 4-8 works inspired by our article since then). State-of-the-art with our algorithm MCTopM + klUCB for multi-player bandits "with sensing", empirical state-of-the-art with our simple (but wrong) "selfish" approach in case of "no sensing"

- Literature review on non stationary models and algorithms, state-of-the-art for piece-wise stationary with our algorithm, GLR test + klUCB

- Literature review on possible use case of doubling trick, plus a unified and more generic analysis of two families of doubling tricks !

### 2019-02-08 2-Chapters/2-Chapter/chapter2.tex
Okay, all the template is better for my need now. I have to write…
Starting to fill the sections of each chapters, to have an overview of the organization
Better outline
Version 0.1

% First chapter begins here
%\adjustmtc
\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}
\chaptermark{Introduction}
\minitoc
\label{chapter:Intro}
\graphicspath{{2-Chapters/1-Chapter/Images/}}

% Write miniTOC just after the title
%\startcontents[chapters]\vbox{\bf\Large Sommaire \hrule}
%\printcontents[chapters]{}{1}{}\vspace*{1pc}\hrule}

% ----------------------------------------------------------------------------
\section*{General context}

\indent
The work presented in this PhD thesis
Blabla

\section*{Contributions}

Blabla

\begin{itemize}
\item Blabla
\item Blabla
\item Blabla
\end{itemize}

\section*{Dissertation outline}
This dissertation is organized as follows.

Blabla

>>>>

% First chapter begins here
\chapter{Single Player and Stationary Multi-Armed Bandit Models}
\label{chapter:2}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/2-Chapter/Images/}}

% ----------------------------------------------------------------------------
\section{Stationary MAB models}
\label{sec:2:notations}

% ----------------------------------------------------------------------------
\subsection{Finite arms and stochastic rewards}

In this thesis, we only consider models with finite arms.
No linear bandits, no contextual bandits etc.

For now, we only consider stochastic rewards. Piece-wise stochastic models are studied in Chapter~\ref{chapter:6}.

% ----------------------------------------------------------------------------
\subsection{Different hypotheses on rewards distributions}

Everything is implemented and documented at
https://smpybandits.github.io/docs/Arms.html

Bernoulli, Gaussian, sub-Bernoulli, sub-Gaussian, Exponential, sub-Exponential...

One dimensional exponential family...

Just bounded, in $[a,b]$ but without loss of generality in $[0,1]$ etc.

Markov models: presented later in Section~\ref{sec:3:markovModels}.

% ----------------------------------------------------------------------------
\section{Applications of stationary MAB}
\label{sec:2:applicationsofStationaryMAB}

\subsection{Various possible applications}

- clinical trial
- A/B testing of websites
- online content recommandation
- wireless communication, lots of possibilities, one is frequency/channel selection in the OSA paradigm, detailed after
- hyper-parameters tuning of deep neural networks etc

\subsection{Applications for Opportunistic Spectrum Access}

Detail the analogy arm = channel in a licensed spectrum, rewards $r_k(t)$ = 1 if no Primary User or 0 if channel $k$ is busy at time $t$.

Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik

% ----------------------------------------------------------------------------
\section{A short review of famous MAB algorithms}
\label{sec:2:famousMABalgorithms}

Everything is implemented and documented at
https://smpybandits.github.io/docs/Policies.html

\subsubsection{Why do we need smart algorithms?}
Why Follow-the-Leader (EmpiricalMeans https://smpybandits.github.io/docs/Policies.EmpiricalMeans.html) don't work, example.

\subsection{Simple but efficient algorithms when well tuned: $\varepsilon$-greedy and Explore-then-Commit}

See
https://smpybandits.github.io/docs/Policies.EpsilonGreedy.html
https://smpybandits.github.io/docs/Policies.ExploreThenCommit.html

% ----------------------------------------------------------------------------
\subsection{Index policies: UCB and others}

\subsubsection{UCB}
Optimism in face of uncertainty, for UCB etc.

\subsubsection{klUCB}
Optimal upper confidence bounds based on Kullback-Leibler divergence and klUCB indexes

\subsubsection{Other policies inspired by UCB}

- UCB-H and klUCB-H
- UCB-V
- UCB-dagger
- UCBoost
- UCB+ and klUCB+

% ----------------------------------------------------------------------------
\subsection{Bayesian policies: Thompson Sampling and others}

Idea behind Thompson sampling and Bayesian philosophy.

The Beta posterior and others (https://smpybandits.github.io/docs/Policies.Posterior.html) and Thompson Sampling.

% ----------------------------------------------------------------------------
\subsection{Other policies: BESA and others}

It's a good opportunity to show off and say that I worked on my own on some non-standard policies.

- One of the first paper I read in 2016 was defining AdBandits, https://smpybandits.github.io/docs/Policies.AdBandits.html, a mixture between Thompson sampling and BayesUCB (very efficient in practice)
- I especially love the BESA algorithm by [? and ? and Maillard].

% ----------------------------------------------------------------------------
\subsection{Policies for adversarial bandits: Exp3 and others}

Exp3, Exp3++ etc
https://smpybandits.github.io/docs/Policies.Exp3.html
https://smpybandits.github.io/docs/Policies.Exp3PlusPlus.html

Softmax: is it the same, but written differently?
https://smpybandits.github.io/docs/Policies.Softmax.html

% ----------------------------------------------------------------------------
\subsection{Hybrid policies: MOSS, klUCB++ and klUCB-Switch and others}

Recent work.
https://smpybandits.github.io/docs/Policies.MOSS.html
https://smpybandits.github.io/docs/Policies.IMED.html
https://smpybandits.github.io/docs/Policies.klUCBPlusPlus.html
https://smpybandits.github.io/docs/Policies.klUCBSwitch.html

Talk about these?
https://smpybandits.github.io/docs/Policies.OCUCB.html
https://smpybandits.github.io/docs/Policies.OSSB.html

With perturbation: maybe we don't need optimism in face of uncertainty, we just need uniform sampling!
Randomized Confidence Bound (RCB) with uniform perturbations performs as well as UCB!
https://smpybandits.github.io/docs/Policies.RandomizedIndexPolicy.html

\subsection{Summary of classification of the most famous algorithms}

A huge table in one page in portrait mode, giving:
- name
- reference, year
- family, classification
- time/memory complexity ?
- regret bound for stochastic regret

of about 20/30 algorithms?

% ----------------------------------------------------------------------------
\section{Lower and upper bounds on regret}
\label{sec:2:lowerUpperBoundsRegret}

\subsection{Measuring performance with the (mean) regret}
Explain what is regret

\subsection{Regret lower bounds}

- [Lai and Robbins] lower-bound in $\Omega(\log(T))$
- Worst case lower in $\Omega(\sqrt{T})$

\subsection{Regret upper bounds, tools and different kinds of bounds}

- useful decomposition, with number of samples (see Claire's PhD)
- different kinds of bounds, problem-dependent with $\bigO{C \log(T)}$ with $C$ a measure of the problem complexity, or problem-independent with $\bigO{\sqrt{KT}}$ ?
- tools to show regret upper-bounds, concentration inequalities,
- short proof of UCB or klUCB? just to start to show the tools

\subsection{Other measures of performances}

- Quantile regret or just histogram of regrets
- Worst case regret (max $R_T^{r}$ for $r$ index of Monte-Carlo simulation?)
- Fairness

% ----------------------------------------------------------------------------
\section{Different approaches on algorithm selection, or ``How to choose your preferred bandit algorithm?''}
\label{sec:2:chooseYourPreferredBanditAlgorithm}

\subsection{Naive approach: use UCB or Thompson sampling, and forget about the rest!}
First solution: be naive, only use UCB everywhere

\subsection{Use prior knowledge about the future application to select beforehand the chosen algorithm}
Second solution, if one has some prior knowledge about the domain or setting for which the learning algorithms will be deployed, she can run synthetic or real-world simulations, compare many algorithms before deployment, and select the best algorithm!

\subsection{Online algorithm selection}

\subsubsection{}
A last solution is online algorithm selection, inspired from expert aggregation.
Include here the discussion about expert aggregation and my \textbf{Aggregator} algorithm, see https://hal.inria.fr/hal-01705292

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter 2}
\label{sec:2:conclusion}

In this chapter, we saw...

Future works include...

% ----------------------------------------------------------------------------
\section{Appendix for Chapter 2}
\label{sec:2:appendix}

\subsection{Numerical computation of Kullback-Leibler divergences and klUCB indexes}

I want to detail the maths behind an implementation of klUCB, see https://smpybandits.github.io/docs/Policies.kullback.html and all what is detailed there.

How to write a fast version of klBern and klucbBern (the two most used functions), using C or Numba or Cython, maybe I can include the speed up simulations here? First piece of code, before really presenting SMPyBandits ?

### 2019-02-08 2-Chapters/3-Chapter/chapter3.tex
Better outline
Version 0.1

% First chapter begins here
\chapter{Presentation of SMPyBandits, a Complete MAB Simulation Library}
\label{chapter:3}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/3-Chapter/Images/}}

@@

% ----------------------------------------------------------------------------
\section{Review of state-of-the-art single-player algorithms}
\label{sec:3:reviewSPAlgorithms}

@@

>>>>

% First chapter begins here
\chapter{SMPyBandits: a state-of-the-art open-source Python library to simulate multi-armed bandit problems}
\label{chapter:3}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/3-Chapter/Images/}}

@@

% ----------------------------------------------------------------------------
\section{Experimental comparisons of state-of-the-art single-player algorithms}
\label{sec:3:reviewSPAlgorithms}

@@

% ----------------------------------------------------------------------------
\section{Appendix for Chapter 3}
\label{sec:3:appendix}

\subsection{Include a minimalist \texttt{main.py} file}

Include verbatim the file
\verb{example_of_main_singleplayer.py}

\subsection{Include a minimalist \texttt{configuration.py} file}

Include verbatim the file
\verb{example_of_configuration_singleplayer.py}

\subsection{Using multi-core to speed-up simulations}

Quickly explain the advantages and drawbacks of using Joblib and joblib.Parallel to run simulations on multiple cores of the same computer

Explain why I didn't try more on parallelisation (eg on Grid5000 or other large scale computer).

### 2019-02-08 2-Chapters/5-Chapter/chapter5.tex
Okay, all the template is better for my need now. I have to write…
Starting to fill the sections of each chapters, to have an overview of the organization
Better outline
Version 0.1

% First chapter begins here
\chapter{Chapter 4 Title}
\label{chapter:4}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/4-Chapter/Images/}}

@@

>>>>

% First chapter begins here
\chapter{Multi-Player Multi-Armed Bandits}
\label{chapter:5}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/5-Chapter/Images/}}

@@

This chapter is basically a raw include from my paper ``Multi-Player Bandits Revisited'', see https://hal.inria.fr/hal-01629733

I also need to include additional simulations from the latest research articles, and discussions about the new works that took inspiration in our paper.

% ----------------------------------------------------------------------------
\section{Towards efficient algorithms solving the "no sensing" case}
\label{sec:5:XXX}

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter 5}
\label{sec:5:conclusion}

In this chapter, we saw...

Future works include...

% ----------------------------------------------------------------------------
\section{Appendix for Chapter 5}
\label{sec:5:appendix}
